Learning to Synthesize Rules for Network Intrusion Detectors

### 2020-03-01 paper/paper.tex
pass table 3

\begin{table*}[t!]
  \small
  \caption{\label{table:attacks}List of attacks. Non-http attacks
    appear at the top; http attacks appear at the bottom.}
  \centering
  \begin{tabular}{llllp{10cm}}
    \toprule
    \multicolumn{1}{c}{Name} &
    \multicolumn{1}{c}{Source} &
    \multicolumn{1}{c}{Type} &
    \multicolumn{1}{c}{Protocol} &
    \multicolumn{1}{c}{Groud Truth (relevant/checked options)} \\
    \midrule
    Black Nurse & \cite{pcap-attacks} & DoS & ICMP & \textbf{icode}:3; \textbf{itype}:3; \textbf{threshold}: type both, track by\_dst, count 250, seconds 1;\\    
    Ping Scan & \cite{netmap} & AREC & ICMP & \textbf{dsize}:0; \textbf{itype}:8; \\
    SYN Flood & \cite{hping3} & DoS & TCP & \textbf{flags}: S,12;
    \textbf{threshold}: type both, track by\_dst, count 5000, seconds
    5;\\
    UDP Teardrop & \Fix{WireShark} & DoS & UDP & \textbf{fragbits}:M; \textbf{id}:124; \\
    UDP Flood & MazeBolt & DoS & UDP & \textbf{fragbits}:M; \textbf{threshold}: type both, track by\_dst, count 5000, seconds
    5; \\
    \midrule
    Apache Struts 2 & \cite{wrccdc} & RCE & HTTP & \textbf{content}:"POST"; http\_method; \textbf{content}:"java.lang.ProcessBuilder"; nocase; http\_client\_body; fast\_pattern; \textbf{content}:"/struts2-rest-showcase/orders/3"; http\_uri; \\    
    ColdFusion \MyComment{PESC} & \cite{nikto} & PESC & HTTP \MyComment{& Privilege Escalation} & \textbf{content}:"GET"; http\_method; nocase; \textbf{content}:"/CFIDE/administrator"; http\_uri; nocase; \\
    iisadmin access\MyComment{web-application-attack} & \cite{nikto} & RCE & HTTP \MyComment{& Adicionar} & \textbf{content}:"/iisadmin"; nocase; http\_uri; \\
    JBoss JMX\MyComment{ Console Beanshell Exploit} & \cite{nikto} & RCE & HTTP \MyComment{& Remote Code Execution} & \textbf{content}:"/HtmlAdaptor"; nocase; http\_uri; \textbf{content}:"action=inspect"; nocase; http\_uri; \textbf{content}:"bean"; nocase; http\_uri; \textbf{content}:"name="; http\_uri; \\
    Script tag in URI\MyComment{Possible Cross Site Scripting Attempt} & \cite{nikto} & RCE & HTTP \MyComment{& Adicionar} & \textbf{content}:"</script>"; nocase; http\_uri; \\
    WeBid \MyComment{Local File Inclusion} & \cite{nikto} & LFI & HTTP & \textbf{content}:"GET "; depth:4; \textbf{content}:"/cron.php?"; http\_uri; nocase; \textbf{content}:"include\_path="; http\_uri; nocase; \textbf{content}:"../"; \\
    WordPress Login & \cite{wrccdc} & PVE & HTTP & \textbf{content}:"log="; http\_client\_body; \textbf{content}:"\&pwd="; http\_client\_body; \textbf{content}:"\&wp-submit="; http\_client\_body; \\
    .htaccess access\MyComment{attempted-recon} & \cite{nikto} & AREC & HTTP \MyComment{& Adicionar} & \textbf{content}:".htaccess"; nocase; http\_uri; \\
    .idq access\MyComment{EXPLOIT ISAPI} & \cite{nikto} & RCE & HTTP \MyComment{& Adicionar} & \textbf{content}:".idq"; nocase; http\_uri; \\
    /system32/ in URI\MyComment{Possible Protected Directory Access Attempt} & \cite{nikto} & AREC & HTTP \MyComment{& Adicionar} & \textbf{content}:"/system32/"; nocase; http\_uri; \\
    \bottomrule
  \end{tabular}
\end{table*}

@@

    \midrule
    Black Nurse & - & - & - & - \\    
    Ping Scan & 6 & 5 & 9 & 1 \\
    SYN Flood & 4 & 2 & 2 & 2 \\
    UDP Teardrop & 1 & 4 & 8 & 3 \\
    UDP Flood & - & - & - & - \\
    \midrule
    Apache Struts 2 & - & - & - & - \\
    ColdFusion & 7 & 19 & 34 & 1\\
    iisadmin access & 3 & 17 & 408 & 1 \\        
    JBoss JMX & 5 & 23 & 228 & 5 \\
    Script tag in URI & 23 & 22 & 786 & 1 \\
    WeBid & 1 & 23 & 11100 & 6\\    
    Wordpress Login & 8 & 59 & - & - \\
    .htaccess access & 5 & 17 & 984 & 2\\
    .idq access & 14 & 19 & 511 & 1 \\
    /system32/ in URI & 4 & 20 & 1,913 & 1 \\
    \bottomrule
  \end{tabular}
\end{table}

>>>>

\begin{table*}[t!]
  \small
  \caption{\label{table:attacks}List of attacks. Non-http attacks
    appear at the top; http attacks appear at the bottom.}
  \centering
  \begin{tabular}{llllp{10cm}}
    \toprule
    \multicolumn{1}{c}{Name} &
    \multicolumn{1}{c}{Source} &
    \multicolumn{1}{c}{Type} &
    \multicolumn{1}{c}{Protocol} &
    \multicolumn{1}{c}{Groud Truth (relevant/checked options)} \\
    \midrule
    Black Nurse & \cite{pcap-attacks} & DoS & ICMP & \textbf{icode}:3; \textbf{itype}:3; \textbf{threshold}: type both, track by\_dst, count 250, seconds 1;\\    
    Ping Scan & \cite{netmap} & AREC & ICMP & \textbf{dsize}:0; \textbf{itype}:8; \\
    SYN Flood & \cite{hping3} & DoS & TCP & \textbf{flags}: S,12;
    \textbf{threshold}: type both, track by\_dst, count 5000, seconds
    5;\\
    UDP Teardrop & \Fix{WireShark} & DoS & UDP & \textbf{fragbits}:M; \textbf{id}:124; \\
    UDP Flood & MazeBolt & DoS & UDP & \textbf{fragbits}:M; \textbf{threshold}: type both, track by\_dst, count 5000, seconds
    5; \\
    \midrule
    Apache Struts 2 & \cite{wrccdc} & RCE & HTTP & \textbf{content}:"POST"; http\_method; \textbf{content}:"java.lang.ProcessBuilder"; nocase; http\_client\_body; fast\_pattern; \textbf{content}:"/struts2-rest-showcase/orders/3"; http\_uri; \\    
    ColdFusion \MyComment{PESC} & \cite{nikto} & PESC & HTTP \MyComment{& Privilege Escalation} & \textbf{content}:"GET"; http\_method; nocase; \textbf{content}:"/CFIDE/administrator"; http\_uri; nocase; \\
    iisadmin access\MyComment{web-application-attack} & \cite{nikto} & RCE & HTTP \MyComment{& Adicionar} & \textbf{content}:"/iisadmin"; nocase; http\_uri; \\
    JBoss JMX\MyComment{ Console Beanshell Exploit} & \cite{nikto} & RCE & HTTP \MyComment{& Remote Code Execution} & \textbf{content}:"/HtmlAdaptor"; nocase; http\_uri; \textbf{content}:"action=inspect"; nocase; http\_uri; \textbf{content}:"bean"; nocase; http\_uri; \textbf{content}:"name="; http\_uri; \\
    Script tag in URI\MyComment{Possible Cross Site Scripting Attempt} & \cite{nikto} & RCE & HTTP \MyComment{& Adicionar} & \textbf{content}:"</script>"; nocase; http\_uri; \\
    WeBid LFI \MyComment{Local File Inclusion} & \cite{nikto} & LFI & HTTP & \textbf{content}:"GET "; depth:4; \textbf{content}:"/cron.php?"; http\_uri; nocase; \textbf{content}:"include\_path="; http\_uri; nocase; \textbf{content}:"../"; \\
    WordPress Login & \cite{wrccdc} & PVE & HTTP & \textbf{content}:"log="; http\_client\_body; \textbf{content}:"\&pwd="; http\_client\_body; \textbf{content}:"\&wp-submit="; http\_client\_body; \\
    .htaccess access\MyComment{attempted-recon} & \cite{nikto} & AREC & HTTP \MyComment{& Adicionar} & \textbf{content}:".htaccess"; nocase; http\_uri; \\
    .idq access\MyComment{EXPLOIT ISAPI} & \cite{nikto} & RCE & HTTP \MyComment{& Adicionar} & \textbf{content}:".idq"; nocase; http\_uri; \\
    /system32/ in URI\MyComment{Possible Protected Directory Access Attempt} & \cite{nikto} & AREC & HTTP \MyComment{& Adicionar} & \textbf{content}:"/system32/"; nocase; http\_uri; \\
    Tomcat server snoop access & \cite{nikto} & AREC & HTTP & \textbf{content}:"/jsp/snp/"; http\_uri; \textbf{content}:".snp"; http\_uri;\\  
    \bottomrule
  \end{tabular}
\end{table*}

@@

    \midrule
    Black Nurse & 1 & 4 & 9 & - \\    
    Ping Scan & 6 & 5 & 9 & 1 \\
    SYN Flood & 4 & 2 & 2 & 2 \\
    UDP Teardrop & 1 & 4 & 8 & 3 \\
    UDP Flood & - & - & - & - \\
    \midrule
    Apache Struts 2 & 2 & 65 & - & - \\
    ColdFusion & 7 & 19 & 34 & 1\\
    iisadmin access & 3 & 17 & 408 & 1 \\        
    JBoss JMX & 5 & 23 & 228 & 5 \\
    Script tag in URI & 23 & 22 & 786 & 1 \\
    WeBid LFI & 1 & 23 & 11100 & 6\\    
    Wordpress Login & 8 & 59 & - & - \\
    .htaccess access & 5 & 17 & 984 & 2\\
    .idq access & 14 & 19 & 511 & 1 \\
    /system32/ in URI & 4 & 20 & 1,913 & 1 \\
    Tomcat Snoop Access & 1 & 24 & 29830 & - \\
    \bottomrule
  \end{tabular}
\end{table}
